%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry} % Document margins

\usepackage{textcomp}
\usepackage{array}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ian Holloway} % Your name
\address{4762 Horseman Dr., Fairborn OH, 45324} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(260) 435-0673 \\ iancholloway@gmail.com} % Your phone number and email

\begin{document}



\begin{rSection}{Citizenship and Clearance}
US Citizen
\\Top Secret Clearance - Contact Riverside Research about additional levels

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Wright State University} - Dayton, OH \hfill {\em August 2016 - December 2019} 
\\ Ph.D - Interdisciplinary Applied Science and Math \hfill {GPA: 3.97}
\\ Thesis Title: Supersonic Euler and Magnetohydrodynamic Flow Past Cones\\
\\{\bf Cedarville University} - Cedarville, OH \hfill {\em August 2012 - May 2016} 
\\ Major: Physics B.S. \hfill { GPA: 3.83 }
\\ Minor: Computer Science, Math \smallskip \\
{\bf Awards} \\ National Merit Scholar | Academic Excellence Scholarship \\ Heyd Math/Science award | Math/Science Department award



\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}

\begin{rSubsection}{Riverside Research - Dayton, OH}{2020-Present}{Computational Scientist}{}
\item Supported development of Asymptotic EM code.
\item Researched and developed a distributed $H^2$ matrix LU factorization and solve for large CEM problems. Prototyped with MPI and UPC++ to run on HPC.
\item Researched and developed a spectral unmixing algorithm with statistical confidence metrics for analysis of HSI data.
\item Researched and developed general low rank compression techniques of Hyper Spectral Imagery (HSI) data tensors to accelerate analysis.
\item Developed an online sequence detection algorithm for compression of long monotonous number streams
\item Contributed to contract proposals and final reports, both customer facing and IRAD.
\end{rSubsection}

\begin{rSubsection}{AFIT - Dayton, OH}{2019-2020}{Research Contractor}{}
\item Investigating the use of Machine learning to accelerate the simulation of the Boltzmann equation, and for defect detection in synthesized materials. 
\item TensorFlow and Keras were the main resources for developing the models.
\end{rSubsection}

\begin{rSubsection}{Applied Optimization - Dayton, OH}{2015-2017}{Applied Math Intern}{}
\item Worked in computational modeling of thermal fluids with application to additive manufacturing.
\item Developed a Genetic Algorithm to fit models to data.
\item Validated simulation results against physical experiments.
\item Developed root-finding algorithms to create a pseudo-inverse for simulations.
\item Applied dimensionless analysis to simulation results to determine scaling relationships.
\item Developed C++, Python, and Visual Basic programs to automate data analysis.
\item Wrote portions of Quarterly reports to contractors and customers.
\item Employed version control techniques, mainly Git.
\item Structured and commented code so it could easily be reviewed by peers.
\end{rSubsection}

\begin{rSubsection}{Wabash Technologies - Huntington, IN}{Summer 2013}{Electrical Engineering Intern}{}
\item Documented and improved the software for a pedal testing apparatus.
\item Assisted with DFMEA.
\item Wrote macros to enhance and automate the test data/spreadsheet management system.
\end{rSubsection}

\begin{rSubsection}{Wright State Univeristy - Dayton, OH}{2020-Present}{Adjunct Professor of Mathematics}{}
\item Taught Differential Equations with Matrix Algebra.
\end{rSubsection}

\begin{rSubsection}{Heartsong Ministries - Cedarville, OH}{2013-2014}{Electric Bass}{}
\item Played bass for a traveling ministry team.
\item Led Bible studies and orchestrated camp activities.
\item Promoted Cedarville University for the Admissions Department
\end{rSubsection}



\end{rSection}

%SKILLS

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Applied Math & Numerical Simulation and Optimization, Statistical Learning, Perturbation \\
Software & Linux, Latex, ParaView, GMSH, OpenSCAD, MS Office \\
Programming & C++, Python + C extensions, Fortran, Matlab, Git, Make \\
Areas of Expertise & CFD, Newtonian Mechanics, Euler equations, Ideal MHD, CEM, Asymptotic EM, HPC \\
Other & Regex \\
\end{tabular}

\end{rSection}

\begin{rSection}{Classes}

{\bf Graduate}\\
\begin{tabular}{ m{15em} m{15em} m{15em} }
Mathematical Modeling & Optimization Techniques	& Applied Mathematics \\
Scientific Computing & Numerical Analysis & Computational Statistics \\
Real Analysis & Hypersonic Flows & Stochastic Processes\\
\end{tabular}

{\bf Undergraduate}\\
\begin{tabular}{ m{15em} m{15em} m{15em} }
Calculus I, II, and III & Computational Physics & Physics I, II, and III \\
Quantum Mechanics & Thermal Physics & Data Structures Using Java \\
Acoustics & Theoretical Mechanics & Linear Algebra \\
Differential Equations & Prob. And Stats & Algorithms \\
Int. and Adv. Physics Lab  & C++ & Foundations of Computer Security
\end{tabular}

\end{rSection}


%    Projects And Seminars

\begin{rSection}{Personal Projects}
{\bf Dissertation research}
\\Used tools from tensor calculus to derive the Euler and Ideal MHD equations in a curved coordinate system
subject to the assumption of conical invariance. Then developed a numerical method to solve the systems. \\
\\{\bf Raspberry Pi Light Board}\\
Developed C++ software to make a Raspberry Pi into a lighting control board for my high school\textquotesingle s auditorium,
allowing presets to be saved and for the lights to be controlled wirelessly.\\
\\{\bf R/C Plane Builds}\\
Designed and built multiple remote controlled airplanes. Arduino, 3D printing, soldering.



\end{rSection}



\end{document}

